%-------------------------
% Resume in Latex
% Author : Harsha Vardhan Bojanki
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://harshabojanki3.github.io/HarshaBojanki.github.io/}{\Large Harsha Vardhan Bojanki}} & Email : \href{mailto:harshabojanki15@outlook.com}{harshabojanki15@outlook.com}\\
  \href{https://harshabojanki3.github.io/HarshaBojanki.github.io/}{https://harshabojanki3.github.io/HarshaBojanki.github.io/} & Mobile : \href{tel:+19379004380}{+1-937-900-4380} \\
  & GitHub : \href{https://github.com/harshabojanki3}{harshabojanki3} \\
  & LinkedIn : \href{https://www.linkedin.com/in/harsha-bojanki}{harsha-bojanki} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Wright State University}{Dayton, OH}
      {Master of Science in Computer Science;  GPA: 3.714}{Aug. 2022 -- April 2024}
    \resumeSubheading
      {Lendi Institute of Engineering and Technology}{AndhraPradesh, India}
      {Bachelor of Engineering in Electronics and Communication Engineering;  GPA: 3.5}{June 2015 -- May 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Wright State University}{Dayton, OH}
      {Graduate Teaching Assistant}{Aug 20 - Present}
      \begin{itemize}
          \item Led lectures, discussions, and labs to enhance student understanding.
          \item ○ Offered one-on-one assistance and constructive feedback.
          \item ○ Collaborated on teaching materials to improve learning
      \end{itemize}
      
    \resumeSubheading
      {WINFACTS TECHNOLOGIES PRIVATE LIMITED}{Bangalore,India}
      {Full-stack Developer}{Jan 2020–Jun 2022}
      \begin{itemize}
          \item Expertise in front-end and back-end technologies, building web interfaces, and developing APIs.
          \item  Collaborated with cross-functional teams and integrated agile and DevOps practices.
          \item Identified and optimized code for performance and troubleshooted technical issues.
      \end{itemize}
      
    \resumeSubheading
      {SERVBIZ SOLUTIONS AND SERVICES PRIVATE LIMITED}{Bangalore,India}
      {Full-stack Developer}{May 2019–Nov 2019}
      \begin{itemize}
          \item Gained hands-on experience in front-end and back-end development technologies. Assisted in building and
          \item maintaining web applications.
          \item Worked closely with experienced developers, participated in code reviews, and learned best practices.
          \item Provided debugging and testing support, actively contributed to project tasks, and assisted in deployment
          \item and maintenance
      \end{itemize}

    \resumeSubheading
      {GR Infotech}{TamilNadu,India}
      {Web Development Intern}{Mar 2019 - May 2019}
      \begin{itemize}
          \item Designed, implemented, and tested web applications, actively participated in development cycles, and adopted new technologies, directly contributing to project success and advancing my web development skills.
      \end{itemize}
\resumeSubheading
      {Spatez Technologies}{Kerala,India}
      {IoT Intern}{April 2018 - Aug 2018}
      \begin{itemize}
          \item Developed and tested firmware, collaborated on design specifications, and explored innovative solutions for IoT and embedded systems, significantly advancing project goals and enhancing my engineering expertise.
      \end{itemize}
   \resumeSubheading
      {Visakhapatnam Steel Plant}{Visakhapatnam,India}
      {Telecommunication Intern}{May 2017 - Aug 2017}   
      \begin{itemize}
          \item Engaged in telecommunications projects, applied electronic and communication engineering principles to solve complex issues, and leveraged cutting-edge technologies, significantly contributing to the enhancement of network performance and my professional growth in telecommunications.
      \end{itemize}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
   \resumeSubItem{Predictive modeling for identifying potentially Hazardous Asteroids}
      {Developed a machine learning model to classify and predict the trajectory of near-Earth objects.Used Python and various data analysis libraries.}
    \resumeSubItem{React Quiz Game App:}
      {Developed a quiz game with a dynamic question flow and real-time scoring. Implemented a seamless UI/UX and integrated APIs for content management}
    \resumeSubItem{Total eCommerce application:}
      {Developed a comprehensive e-commerce platform, enhancing
customer engagement and sales.}
    \resumeSubItem{AN RADIX-2 FFT ARCHITECTURE:}
      {Designed architecture for processing twin data streams for
MIMO systems, improving efficiency.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\begin{itemize}[noitemsep]
    \item \textbf{Front-End:} HTML, CSS, JavaScript, React.js, Responsive Web Design
    \item \textbf{Back-End:} C\#.NET, JavaScript, SQL, Node.js
    \item \textbf{Database:} SQL, Database-driven Web Apps
    \item \textbf{Version Control:} Git, GitHub, Git BASH
    \item \textbf{Cloud Services:} Amazon Web Services (AWS)
    \item \textbf{IDEs:} Visual Studio
    \item \textbf{Sys. Admin:} Linux, Ubuntu
    \item \textbf{Telecom:} Radio Frequency (RF), Frequency Analysis
    \item \textbf{Languages:} Java, C\#.NET
    \item \textbf{Web Design \& Soft Skills:} Web Design, Web Apps; Communication, Quality, Testing, Debugging, Security
\end{itemize}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
